---
title: "Methods"
---

```{r}

# Loading packages
library(tidyverse) #data manipulation
library(haven) #imports SPSS file
library(scales) #wrap long labels on charts
library(grid)
library(gridExtra) #combine different plots in one image
library(gt) #formatted tables


# Importing working dataset
df_ucd <- read_sav("data/UCD_Survey_20221217.sav")

# Derived variables

# Demographic
df_ucd$female <- if_else(df_ucd$demgender == 2, "Female", "Others")
df_ucd$cossl <- if_else(df_ucd$demcollege == 5, "CoSSL", "Others")
df_ucd$year1 <- if_else(df_ucd$demyear == 1, "First Year", "Others")

#Knowledge
df_ucd$knowsmth <- if_else(df_ucd$knhowmuch %in% c(3, 4), "lot/moderate", "little/nothing")
df_ucd$easyknezcntry <- if_else(df_ucd$knezcntry %in% c(3, 4),  1, 0)
df_ucd$easyknezexplco2 <- if_else(df_ucd$knezexplco2 %in% c(3, 4), 1, 0)
df_ucd$easyknezrefugee <- if_else(df_ucd$knezrefugee %in% c(3, 4),  1, 0)

#Anxiety
df_ucd$anxday <- if_else(df_ucd$anxthink %in% c(6, 7), 1, 0)
df_ucd$anxweek <- if_else(df_ucd$anxthink > 3, 1, 0)
df_ucd$veryworried <- if_else(df_ucd$anxworry %in% c(1, 7), 1, 0)


```


```{r}
# Function to get rounded percentage value for valid observations
get_perc <- function(variable, value){
    numerat <- sum(df_ucd[[variable]] == value, na.rm = T)
    denominat <- sum(!is.na(df_ucd[[variable]]))
    paste0(round(numerat/denominat*100), "%")
    }

# Function to get percentages by groups
get_perc_grp <- function(mainvar, mainvalue, group, grpvalue){
    df_new <- df_ucd[df_ucd[[group]] == grpvalue,]
    numerat <- sum(df_new[[mainvar]] == mainvalue, na.rm = T)
    denominat <- sum(!is.na(df_new[[mainvar]]))
    paste0(round(numerat/denominat*100),"%")
}
    
```

Scientific research relies substantially on social surveys to assess knowledge, attitudes and action in relation to climate change issues. The objective of the current project was to develop and test an instrument to measure students’ understandings of, attitudes towards and actions against climate change to establish a baseline for larger research projects on Climate Change Education in Higher Education.

The initial questionnaire was designed in September 2021 and included questions tested in previous surveys with higher education students. The pre-test was administered in October 2021 with 15 graduate students from the School of Education. Participants generally provided positive feedback in relation to the length of the questionnaire and the clarity of the questions. Four questions were reformulated due to their length and difficulty in responding using a smartphone.

We recruited undergraduate participants using social media and in class announcements facilitated by module coordinators with the permission of the head of each School. The survey was taken by `r nrow(df_ucd)` undergraduate students during the months of October and November 2022.  On average, it took `r round(mean(df_ucd$admdurat)/60)` minutes to be completed.  

## Participant demographics

Here is some information about the participants in the survey:

- **`r get_perc("demgender",1)`** of respondents identified as male, **`r get_perc("demgender",2)`** identified as female, and **`r get_perc("demgender",3)`** as non-binary;

- **`r get_perc("demurbrur",2)`** of students that responded the survey grew up in a rural area.

- **`r get_perc("demnat",1)`** of respondents identified as Irish, **`r get_perc("demnat",2)`** indicated another European nationality, and **`r get_perc("demnat",3)`** another non-European nationality; 

- The majority of students came from the College of Engineering and Architecture (**`r get_perc("demcollege",3)`**) and the College of Social Sciences and Law  (**`r get_perc("demcollege",5)`**). 

- Most students were in their first (**`r get_perc("demyear",1)`**) or second (**`r get_perc("demyear",2)`**) year at UCD.

- **`r get_perc("demschgreen",1)`** of students declared that they attended a [Green-School](https://greenschoolsireland.org) in Ireland (i.e. with a green flag), whereas **`r get_perc("demschgreen",2)`** attended a secondary school in Ireland that was not a green school, and (**`r get_perc("demschgreen",4)`**) did not know if their school was a Green-School. 

